\href{/files/Jovan_Markov_CV.pdf}{Download PDF version of my CV}

\{\% include base\_path \%\}

\section{Education}\label{education}

\begin{itemize}
\tightlist
\item
  2022 -- present: Weizmann Institute of Science, Physics, PhD, Quantum
  computing and quantum simulation, Advisor: Prof.~Roee Ozeri.
\item
  2019 -- 2021: Weizmann Institute of Science, Physics, MSc, Advisor:
  Prof.~Kfir Blum.
\item
  2015 -- 2019: Faculty of Physics, University of Belgrade, Theoretical
  and Experimental Physics, BSc. GPA -- 9.79/10
\end{itemize}

\section{Skills}\label{skills}

\begin{verbatim}
<ul>
  <li>Git</li>
  <li>Jupyter Notebook</li>
  <li>LaTeX</li>
  <li>Linux command line</li>
  <li>Mathematica</li>
  <li>Matlab</li>
  <li>Python</li>
  <li>ROOT</li>
</ul>
\end{verbatim}

\begin{verbatim}
<ul>
  <li>Event Planning</li>
  <li>Outreach</li>
  <li>Public Speaking</li>
  <li>Presenting</li>
  <li>Project Management</li>
  <li>Seminar Organization</li>
</ul>
\end{verbatim}

\section{Publications}\label{publications}

\{\% for post in site.publications reversed \%\} \{\% include
archive-single-cv.html \%\} \{\% endfor \%\}

\section{Teaching, Organizing}\label{teaching-organizing}

\begin{itemize}
\tightlist
\item
  2024 -- 2025: Organizer of The AMOS Seminar, Faculty of Physics and
  Faculty of Chemistry, Weizmann Institute of Science. A weekly seminar
  for journal clubs, invited speakers, and PhD defenses.
\item
  2020 -- 2022: Tutor, Faculty of Physics, Weizmann Institute of
  Science. Helping new MSc students with coursework.
\end{itemize}

\section{Languages}\label{languages}

\begin{itemize}
\tightlist
\item
  Serbian, Native.
\item
  English, Fluent, TOEFL iBT Score:110/120 (Nov 2018).
\item
  Hebrew, Elementary.
\end{itemize}

\section{Conferences, Seminars, Talks,
Posters}\label{conferences-seminars-talks-posters}

\begin{itemize}
\item
  2025: ECTI 2025, European Conference on Trapped Ions. Poster: Digital
  predistortion of optical field of a fast and high-fidelity entangling
  gate for trapped ion qubits. Authors: J. Markov, Y. Shapira, N.
  Akerman, R. Ozeri. \href{https://www.ecti2025.com/home}{Conference
  website}
\item
  2025: Petnica Science Center, Physics Seminar, Valjevo, Serbia.
  Workshop: Quantum Computing Workshop (two-day, 8-hour hands-on course
  based on
  \href{https://www.cl.cam.ac.uk/teaching/1819/QuantComp/materials.html}{Cambridge
  Quantum Computing syllabus}, plus trapped ion quantum computing and
  lab tour)
\item
  2023: Annual New Year Seminar, Faculty of Physics, University of
  Belgrade, Serbia. Talk: Quantum computers and what to do with them.
  (in Serbian)
\item
  2023: 54th Annual Meeting of the APS Division of Atomic, Molecular and
  Optical Physics, Spokane, Washington. Talk: Digital predistortion of
  optical field of a fast and high-fidelity entangling gate for trapped
  ions qubits. Authors: \textbf{JM}, Yotam Shapira, Nitzan Akerman, Roee
  Ozeri.
\item
  2023: 25th Annual SQuInT Workshop, Albuquerque, New Mexico. Poster:
  Programmable quantum simulations on a trapped-ions quantum computer
  with a global drive. Authors: \textbf{JM}, Yotam Shapira, Nitzan
  Akerman, Ady Stern, Roee Ozeri.
\item
  2018: IPPOG CMS Masterclass, Belgrade, Serbia. Helping participants
  with hands-on data-analysis exercises.
\end{itemize}

\section{Projects, Internships}\label{projects-internships}

\begin{itemize}
\tightlist
\item
  2021: MSc thesis, Project: Ultralight dark matter: Ground state
  solutions in the presence of two fields, Advisor: Prof.~Kfir Blum.
\item
  2019: Summer Student Program, CERN, Geneva, Switzerland. Project:
  \href{https://cds.cern.ch/record/2687408/files/Jovan_Markov_CERN_Summer_School_2019_project_report\%20final.pdf}{Top
  quarks in the lepton + jets channel in PbPb collisions}. Mentors
  (CMS): Pedro Ferreira daSilva, Émilien Chapon.
\item
  2017: Summer Research Student, Weizmann Institute of Science, Rehovot,
  Israel. Kupcinet-Getz International Summer School, Mentor (ATLAS)
  Prof.~Alexander Milov. Studied the production of Z bosons in the
  di-electron decay channel in proton-proton (pp) collisions which was
  measured in the ATLAS detector. The results from pp collisions were
  compared to the previously measured data in the proton-lead (p-Pb)
  collisions system at the same energy. Information on the nuclear
  modification factor \{\% raw \%\}\(RpPb\)\{\% endraw \%\}, for Z
  bosons in p-Pb collisions was extracted from the comparison. The whole
  data analysis was done by writing C++ scripts using ROOT.
  \href{http://www.weizmann.ac.il/particle/atlas/sites/particle.atlas/files/uploads/heavy-ion-physics.pdf}{Booklet}
  with our projects.
\item
  2014 -- 2015: High school Physics program, Petnica Science Center,
  Valjevo, Serbia. Project: Determining the mass of the \{\% raw
  \%\}\(K_S^0\), \(\pi^+\), and \(\pi^-\)\{\% endraw \%\} mesons using
  the Theil index. Mentors (LHCb): Vladimir Gligorov, Miriam Lucio
  Martinez, Diego Martinez Santos.
\item
  2013: High school Physics program, Petnica Science Center, Valjevo,
  Serbia. Project: Examination of properties of hydraulic jumps.
  Mentors: Vladan Pavlović, Marija Janković.
\end{itemize}

\section{Training/Courses}\label{trainingcourses}

\begin{itemize}
\tightlist
\item
  2015: IPPOG CMS Masterclass in Belgrade, Serbia
\item
  2015: Introduction to programming with MATLAB, Vanderbilt University
  (Coursera)
\item
  2014: LHCb Masterclass, Petnica Science Center, held by Vladimir
  Gligorov (LHCb collaboration)
\end{itemize}

\section{Memberships}\label{memberships}

\begin{itemize}
\tightlist
\item
  2015 -- present: EMINETER - student organization of the Faculty of
  Physics, Belgrade University
\item
  since 2015: Mathematical Grammar School Alumni Society (ALMAGI)
\item
  2017, 2018, 2024: Serbian Physical Society
\item
  2020 -- present: Israel Physical Society
\item
  2023: American Physical Society
\end{itemize}

\section{Awards}\label{awards}

\begin{itemize}
\tightlist
\item
  2016: 1st place at student research paper competition in physics, at
  Primatiyada 2016, regional event for students from Natural Science and
  Mathematics faculties, held in Albena, Bulgaria.
\item
  2015: ``Vuk Karadi'' diploma, Ministry of Education of the Republic of
  Serbia.
\item
  2012 -- 2015: Won 3rd prize four years in a row at the national level
  highschool physics competition, organized by the Serbian Physical
  Society.
\end{itemize}

\section{Scholarships}\label{scholarships}

\begin{itemize}
\tightlist
\item
  2015 - 2019: Scholarship for exceptionally gifted high school and
  university students, awarded by the Ministry of Education, Science and
  Technological Development of the Republic of Serbia.
\item
  2013 - 2016: Scholarship given to high school students for their
  achievements on the national and international competitions during the
  previous calendar year, awarded by the Fund for Young Talents of the
  Republic of Serbia.
\item
  2013: Scholarship given to high school students for their achievements
  on the renowned competitions at home and abroad during the year 2012,
  awarded by The City Of Belgrade - City Administration.
\end{itemize}

\section{Other engagements}\label{other-engagements}

\begin{itemize}
\tightlist
\item
  2016 - present: Assistant at the Physics program,
  \href{http://petnica.rs/}{Petnica Science Center}, Serbia. Giving
  lectures and helping high school students working on research
  projects.
\item
  2024: Reviewer of 4th Grade problem sets, High School Physics
  Competitions (academic year 2023/24), organized by the Serbian
  Physical Society.
\item
  2017 -- 2018: Member of committee at the National Physics Competition,
  organized by the Serbian Physical Society.
\item
  2015 -- 2019: Engaged in science promotion activities with Faculty of
  Physics, University of Belgrade, demonstrating physics experiments at
  schools all across Serbia.
\item
  2014 -- 2019: Journalist and speaker for ``Step towards science''
  radio show, at the national radio station Radio Belgrade 1, with my
  own segment ``And that's physics'', where I talk about a certain topic
  from physics.
\item
  2013 -- 2019: Science Demonstrator, Center for the Promotion of
  Science, Belgrade, Serbia.
\item
  2012 -- 2017: Researchers Night (part of European Researchers Night
  project), Belgrade, Serbia. Organized several exhibits over the years.
  Also participated in demonstrating popular science experiments since
  2012.
\item
  2012 -- 2018: Serbian Science Festival, Belgrade, Serbia. Organized
  for several years the ``Experteenager zone'', part of the Festival
  where high schools participate. Organized several exhibits. Also
  participated in demonstrating popular science experiments since 2012.
\item
  2012 -- 2017: Initiated and organized a School Science Festival, at my
  former Elementary school, which has been held for five consecutive
  years and has been seen by several thousand visitors. It has more than
  80 exhibits which I made myself.
\item
  2010 -- 2017: Writer at Viva fizika (Viva physics), a science
  popularization web portal in physics and astronomy.
\end{itemize}

\section{Other Interests}\label{other-interests}

\begin{itemize}
\tightlist
\item
  Hiking
\item
  Photography
\item
  Digital art
\item
  History
\item
  Language geek
\end{itemize}

\section{References}\label{references}

\begin{itemize}
\tightlist
\item
  Kfir Blum, Professor, Weizmann Institute of Science, Israel
\item
  Alexander Milov, Professor, Weizmann Institute of Science, Israel
\item
  Vladimir Gligorov, research scientist (CRCN grade), CNRS, France
\end{itemize}

\section{Talks}\label{talks}

\{\% for post in site.talks reversed \%\} \{\% include
archive-single-talk-cv.html \%\} \{\% endfor \%\}
